---
title: "Visualisation of Full Sample Precision Analysis Results"
author: "Anna T. Wittmann"
date: today
format:
  html:
    code-fold: false
    highlight-style: haddock
    theme: flatly
    toc: true
    toc-location: left
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false
# Turn off scientific notation globally
options(scipen = 999)
```

# Dependencies

```{r}
# packages and setup here

#load simulation results
full_simulation_unnested <- readRDS("../../data/raw/precision_analysis/full_simulation_unnested.rds") 
#load data for estimates and ci
simulation_ci_estimates <- readRDS("../../data/processed/precision_analysis/simulation_ci_estimates.rds")

library(kableExtra)
library(ggplot2)
library(viridis)
library(patchwork)
library(scales) # breaks pretty
library(dplyr) # for %>% 
library(apa7)
library(flextable)
```
# Inspect parameters with CIs smaller than 0.05

```{r}
simulation_ci_estimates %>% 
  filter(ci_width_prob <=0.05) %>% 
  count()
# 150/315 unique parameter combinations have CI narrower than 0.05 

simulation_ci_estimates %>% 
  filter(ci_width_prob<=0.05) %>% 
  group_by(sample_size) %>% 
  count() %>% 
  kable() %>% 
  kable_classic(full_width = FALSE)
```
150/315 parameter combinations have CIs narrower than or equal to 0.05. Sample size (n_ci_0.05/n_total): 40(11/45); 50(17/45); 60(20/45), 70(24/45); 80-100(26/45). Descriptively speaking, there seams to be no significant increase in precision above 80 papers. The next question is for which sample size.

## apa7 table

```{r}
set_flextable_defaults(
  theme_fun = theme_apa,
  font.family = "Times New Roman",
  text.align = "center",
  table_align = "left"
)

simulation_ci_estimates %>% 
  filter(ci_width_prob<=0.05) %>% 
  group_by(sample_size) %>% 
  count() %>% 
  flextable() %>% 
  save_as_image(path = "../../data/outputs/plots/n_table.png")

```


# Visually inspect differences between sample sizes

```{r}
p40 <- simulation_ci_estimates %>% 
  mutate(paper_random_effect = as.factor(paper_random_effect),
         sample_size = as.factor(sample_size),
         effect_size = as.factor(effect_size)) %>% 
  
  filter(sample_size == 40) %>% 
  
  ggplot(aes(x = effect_size, 
             y = ci_width_prob, 
             color = paper_random_effect))+
  labs (title = "N = 40", 
        x = "Effect size",
        y = "CI width [decimal]",
        color = "Paper effect")+
  geom_point(alpha = 1)+
  geom_hline(yintercept = 0.05, 
             color = "hotpink4", 
             linetype = "dashed")+
  theme_grey()+
  scale_color_viridis_d(direction = 1, 
                        option = "D")

p50 <- simulation_ci_estimates %>% 
  mutate(paper_random_effect = as.factor(paper_random_effect),
         sample_size = as.factor(sample_size),
         effect_size = as.factor(effect_size)) %>% 
  
  filter(sample_size == 50) %>% 
  
  ggplot(aes(x = effect_size, 
             y = ci_width_prob, 
             color = paper_random_effect))+
  labs (title = "N = 50", 
        x = "Effect size",
        y = "CI width [decimal]",
        color = "Paper effect")+
  geom_point(alpha = 1)+
  geom_hline(yintercept = 0.05, 
             color = "hotpink4", 
             linetype = "dashed")+
  theme_grey()+
  scale_color_viridis_d(direction = 1, 
                        option = "D")

p60 <- simulation_ci_estimates %>% 
  mutate(paper_random_effect = as.factor(paper_random_effect),
         sample_size = as.factor(sample_size),
         effect_size = as.factor(effect_size)) %>% 
  
  filter(sample_size == 60) %>% 
  
  ggplot(aes(x = effect_size, 
             y = ci_width_prob, 
             color = paper_random_effect))+
  labs (title = "N = 60", 
        x = "Effect size",
        y = "CI width [decimal]",
        color = "Paper effect")+
  geom_point(alpha = 1)+
  geom_hline(yintercept = 0.05, 
             color = "hotpink4", 
             linetype = "dashed")+
  theme_grey()+
  scale_color_viridis_d(direction = 1, 
                        option = "D")

p70 <- simulation_ci_estimates %>% 
  mutate(paper_random_effect = as.factor(paper_random_effect),
         sample_size = as.factor(sample_size),
         effect_size = as.factor(effect_size)) %>% 
  
  filter(sample_size == 70) %>% 
  
  ggplot(aes(x = effect_size, 
             y = ci_width_prob, 
             color = paper_random_effect))+
  labs (title = "N = 70", 
        x = "Effect size",
        y = "CI width [decimal]",
        color = "Paper effect")+
  geom_point(alpha = 1)+
  geom_hline(yintercept = 0.05, 
             color = "hotpink4", 
             linetype = "dashed")+
  theme_grey()+
  scale_color_viridis_d(direction = 1, 
                        option = "D")

(p40+p50)/(p60+p70) + plot_layout(guides = "collect")
```
# Comparing samples 80 to 100

```{r}
p80 <- simulation_ci_estimates %>% 
  filter(sample_size == 80) %>% 
  
  ggplot(aes(x = effect_size, 
             y = ci_width_prob, 
             color = paper_random_effect))+
  labs(title = "N = 80", 
        x = "Effect Size",
        y = "CI Width [Decimal]",
        color = "Paper Effect")+
  geom_point(alpha = 1)+
  scale_x_continuous(
    breaks = seq(0, 1, by = 0.1))+
  scale_y_continuous(
    breaks = seq(0, 0.125, by = 0.025))+
  coord_cartesian(
    xlim = c(0, 1),
    ylim = c(0, 0.125)
  )+
  geom_hline(yintercept = 0.05, 
             color = "hotpink4", 
             linetype = "dashed")+
  theme_grey()+
  scale_color_viridis_c(breaks = seq(0.1, 0.9, by = 0.2),
                        direction = 1,
                        end = 0.9,
                        option = "D")+
  theme(text=element_text(size=10,  family="sans"))


p90 <- p40 <- simulation_ci_estimates %>% 
  mutate(paper_random_effect = as.factor(paper_random_effect),
         sample_size = as.factor(sample_size),
         effect_size = as.factor(effect_size)) %>% 
  
  filter(sample_size == 90) %>% 
  
  ggplot(aes(x = effect_size, 
             y = ci_width_prob, 
             color = paper_random_effect))+
  labs (title = "N = 90", 
        x = "Effect size",
        y = "CI width [decimal]",
        color = "Paper effect")+
  geom_point(alpha = 1)+
  geom_hline(yintercept = 0.05, 
             color = "hotpink4", 
             linetype = "dashed")+
  theme_grey()+
  scale_color_viridis_d(direction = 1, 
                        option = "D")

p100 <- simulation_ci_estimates %>% 
  mutate(paper_random_effect = as.factor(paper_random_effect),
         sample_size = as.factor(sample_size),
         effect_size = as.factor(effect_size)) %>% 
  
  filter(sample_size == 100) %>% 
  
  ggplot(aes(x = effect_size, 
             y = ci_width_prob, 
             color = paper_random_effect))+
  labs (title = "N = 100", 
        x = "Effect Size",
        y = "CI Width [decimal]",
        color = "Paper Effect")+
  geom_point(alpha = 1)+
  geom_hline(yintercept = 0.05, 
             color = "hotpink4", 
             linetype = "dashed")+
  theme_grey()+
  scale_color_viridis_d(direction = 1, 
                        option = "D")

p80+p90/p100 + plot_layout(guides = "collect")
```
# Save N = 80 plot
```{r}
p80
ggsave("../../data/outputs/plots/p80.png")
```

# Session info

```{r}
sessionInfo()
```
