---
title: "Correction to: Main Data Processing"
author: "Anna T. Wittmann"
date: today
format:
  html:
    code-fold: false
    highlight-style: haddock
    toc: true
    toc-location: left
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false
# Turn off scientific notation globally
options(scipen = 999)
rm(list = ls())
```

::: callout-caution
This is the script outlining the discovery of my filtering error in the original version of my thesis. Beneath each chunk, I will add a box (just like this one) detailing the steps I took to identify the filtering error highlighted by Malte Elson. The error caused inconsistencies in the reported (sub-)sample sizes reported in the thesis. For a detailed explanation refer to the updated thesis document. To ensure maximum clarity, I added clearly identified sanity checks along the way.
:::

# Dependencies

```{r}
# packages and setup 
library(dplyr) # NOTE: needs dplyr version >= 1.2.0 for recode_values() 
library(janitor)
library(kableExtra)
library(readr)
library(stringr)
library(waldo)

```

# Read in Data from CodeBot's Combined Reports & Rough Cleanup

```{r}
#| output: false

# save file paths to vector
files <- dir("../../data/raw/main/adjudicator/combined_reports", 
             full.names = TRUE)  |>  
  dput()

# save first authors to vector
author <- dir("../../data/raw/main/adjudicator/combined_reports", 
              full.names = FALSE) |> 
  dput() |>
  str_remove_all("_combined_report.csv")

# paper_id
paper_id <-  c(1:17)

# read in all .csv() files and combine to one df
df <- read_csv(files, 
               id = "filename",
               na = "null",
               locale = locale(encoding = "UTF-8")) |> 
  # add author column
  mutate(paper_id = dplyr::recode_values(filename, 
                                         from = files, 
                                         to = paper_id),
         # without the dplyr:: there appears to be a namespace collision
         author = dplyr::recode_values(filename, 
                                       from = files, 
                                       to = author)) |>
  # move author column to the front
  relocate(c(author,paper_id), .after = filename)

```

```{=html}
<style>
.table {
  width: auto !important;
  margin: 0 auto !important}
</style>
```

```{r}

# NEW sanity check #
df |> count(codebot_human_agreement) |> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(human_match_judgement) |> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(codebot_match_judgement) |> 
  kable() |> 
  kable_styling()
```

::: callout-caution
Prior to any processing, the number of valid \[1,0\] codebot_human_agreement ratings was 1002.
:::

# Check for Empty Rows

This check was predefined in the pre-registration.

```{r}
# remove empty rows
test <- df |> janitor::remove_empty(which = "rows")

# compare df with and without the empty rows
compare(test,df)

# remove from environment
rm(test) 
```

# Check for Human Error in Manually Coded Entries

After visually inspecting the data, it is evident that there are multiple sources of minor, fixable errors introduced by a) manual coding, b) working with the .csv files across different operating systems c) the adjudication programming. The following reflects my attempt to clean up the data as best as I can with the limitation that there is no second set of eyes to validate my approach. Rows containing (minorly) modified observations will get flagged in a separate boolean variable *corrected*. Another boolean variable (*exclude*) will flag observations with major issues that warrant exclusion from the inferential analyses. See below a list of spotted data quality issues after visually inspecting the data and comparing it to the sample_coding_human.xlsx file.

::: callout-caution
While the first source of error was anticipated in the pre-registration, this was not the case for the latter two. However, I consider the assessment of the latter error sources to be crucial for the validity of the results which is why I will flag them during processing.
:::

**List of observed errors:**

- In the data from Hsieh et al., the columns manuscript_content through results for the inference criteria were coded as `NA\r\n`. Since the `\r\n` part are Window's "invisible" characters signaling Carriage Return `\r` and Line Feed `\n`, they create the weird situation where those cells are neither recognized by is.na() nor by directly filtering for "NA". Apparently, read_csv() also did not recognize them as NA_characters and neither did the adjudicator which was supposed to replace rows which only had NAs with empty strings throughout. NA:NA in human_code_location resulted from the adjudicator aggregating across the given file and code line quote. This should also be empty instead of NA. -\> Change these cells to "" (because the NA coding needs to be fixed later).

- Inconsistent use of delimiters when it comes to manuscript location quotes - Missing manuscript content in cases where manuscript location and a judgement are given and a comparison to the original excel sheet makes it evident that there must have been a copy & paste error involved -\> Flag but do not correct because this would alter the adjudicator's judgement.

- Dimensions were numbered for clarity during manual coding, not all numbers were removed.

## Clean Hsieh

```{r}
# select all relevant columns coded by human
col_check <- df |> 
  colnames() |> 
  as_tibble() |> 
  filter(str_starts(value,"human")) |> 
  pull() |> 
  # exclude all but the judgement variable because this has separate issues
  head(-1) 

df <- df |> 
  mutate(
    # add transparency column
    corrected = if_else(human_manuscript_content == "NA\r\n", TRUE, FALSE),
    # mutate the hsieh columns
    across( # does the operation across all columns given in...
      all_of(col_check), # all_of makes sure that all columns in the vector are matched 
      ~ case_when(.x %in% c("NA\r\n", "NA:NA") ~ "", 
                  .default = .x)))

# sanity check 
df |> filter(human_manuscript_content == "NA\r\n") |> 
  nrow()
```

```{r}

# NEW sanity check #
df |> count(codebot_human_agreement) |> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(human_match_judgement) |> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(codebot_match_judgement) |> 
  kable() |> 
  kable_styling()
```

::: callout-caution
The number of valid \[1,0\] codebot_human_agreement ratings is still 1002. The number of each raters' valid \[1,0\] match judgements also remains unchanged.
:::

The NAs that got read in in an unwanted manner were successfully removed and replaced with empty strings.

## Clean up Dimension

```{r}
df |> group_by(dimension) |> 
  count(dimension) |> 
  kable() |> 
  kable_styling()

df <- df |> 
  mutate(corrected = if_else(str_detect(dimension, "\\d"), TRUE, FALSE),
         dimension = str_remove(dimension,"\\d"))

df |> group_by(dimension) |> 
  count(dimension) |> 
  kable() |> 
  kable_styling()
```

```{r}

# NEW sanity check #
df |> count(codebot_human_agreement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(human_match_judgement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(codebot_match_judgement)|> 
  kable() |> 
  kable_styling()
```

::: callout-caution
The number of valid \[1,0\] codebot_human_agreement ratings is still 1002. The number of each raters' valid \[1,0\] match judgements continues to remain unchanged.
:::

## Clean Up Manuscript Location

In a next step I will clean up human_manuscript_location so that I can properly screen for unintentionally blank cells in human_manuscript_content.

```{r}
# View unique values
df |> 
  group_by(human_manuscript_location) |> 
  count() |> 
  kable() |> 
  kable_styling()
```

This variable should only hold values \\in (0,1,2,"")\$. The 3 needs manual inspection since it is most likely due to a copy paste error, the "." need to become ";" and all spaces need to be removed.

```{r}
# removing spaces and replacing dots with semicolons
df <- df |>  
  mutate(corrected = case_when(str_detect(human_manuscript_location, 
                                          "[[:blank:]]") 
                               ~TRUE,
                               str_detect(human_manuscript_location, 
                                          "\\.") 
                               ~TRUE,
                               # visual inspection shows that the 3 should have been a two
                               human_manuscript_location == "3" 
                               ~TRUE,
                               .default = FALSE),
         human_manuscript_location = case_when(str_detect(human_manuscript_location, 
                                                          "[[:blank:]]")
                                               ~gsub(" ","", 
                                                     human_manuscript_location),
                                               str_detect(human_manuscript_location, 
                                                          "\\.")
                                               ~gsub("\\.",";", 
                                                     human_manuscript_location), 
                                               # . is "wildcard" so regex needs to escape this by \\
                                               human_manuscript_location == "3" 
                                               ~"2",
                                               .default = human_manuscript_location
         ))

# View unique values
df |> 
  group_by(human_manuscript_location) |> 
  count() |> 
  kable() |> 
  kable_styling()
```

```{r}

# NEW sanity check #
df |> count(codebot_human_agreement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(human_match_judgement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(codebot_match_judgement)|> 
  kable() |> 
  kable_styling()
```

::: callout-caution
The number of valid \[1,0\] codebot_human_agreement ratings is still 1002. The number of each raters' valid \[1,0\] match judgements continues to remain unchanged.
:::

Screening for human_manuscript_content cells unintentionally left blank.

```{r}
df |> 
  filter(human_manuscript_content == "" & str_detect(human_manuscript_location,"\\d")) |> 
  kable() |> 
  kable_styling(full_width = FALSE) |> 
  scroll_box(width = "100%", height = "400px")
```

In case of Berger et el., there are 3 misplaced location quotes, all for the variable "single item america" as is evident from the sample_coding_human.xlsx which should be empty strings instead. Carvalho et al. is missing the following transformation quote: "Accuracy by question type and a total score was calculated". Going back to the paper, the Evans quote is wrong since there was no mention of a transformation to be found. Going back to Helm revealed, that there were multiple problematic lines. For Analysis 2, the inference criterion is in fact not evident from the text. The inference criterion for Analyses 3 and 4 should be "95% CI". For Mancassola, the quotes for variable specification are missing in analyses 5 to 8 due to a manual copy pasting error since they required the same quote as the model specification which is always given.

::: callout-note
I will not fill the blanks for manuscript content since their absence impacted the adjudicator's judgement. I also choose not to correct the respective adjudicator's judgements manually, because I cannot account for possible distortion of the adjudicator's ratings. Instead, I will mark them as to be excluded in the GLMM analysis.
:::

```{r}
# add exclusion variable
df <- df |>  
  mutate(exclude = if_else(human_manuscript_content == "" &
                             str_detect(human_manuscript_location,"\\d"),
                           TRUE,
                           FALSE))

# sanity check
df |> 
  filter(exclude == TRUE) |> 
  count() |> 
  pull() 
```

```{r}

# NEW sanity check #
df |> count(codebot_human_agreement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(human_match_judgement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(codebot_match_judgement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> filter(exclude == FALSE) |> 
  count(codebot_human_agreement)|> 
  kable() |> 
  kable_styling()
```

::: callout-caution
The number of valid \[1,0\] codebot_human_agreement ratings is now **1001**. This is in accordance with the value reported in the thesis. The number of valid \[1,0\] human and CodeBot match judgements remains unchanged.
:::

# Sanity Check NAs

Currently, there is an issue with the meaning of NAs across the 3 judgement variables.

**Human_match_judgement** takes on this value both when manuscript information is present and when it is not. This should not be the case as an NA in the sense of "indecisiveness" is different from NA in the sense of missingness. I will change meaningful NAs to 99 and cases where there is no manuscript content coded to NA. Once the match variable has been transformed, I will replace human_match_judgement with NA whenever no quote was provided so that NA truly reflects absence and 99 uncertainty.

**Codebot_match_judgement** takes on the values 1/0/NA and there are no empty string entries by CodeBot. Thus the match judgement will become 99 in cases where it was previously NA.

**Codebot_human_agreement** is currently NA in cases where both raters rated "meaningful" NA but also NA when one rater's info is missing. Cases where one rater's rating is missing should stay NA because it indicates the absence of assessable agreement, but cases where both raters coded info and judged "meaningful" NA, the adjudicator's rating should be 99.

## Human_match_judgement

```{r}
# sanity check
pre <- df |> filter(!human_manuscript_content == "" & is.na(human_match_judgement)) |>
  count()

# differentiate between meaningful and meaningless NAs
df <- df |> 
  mutate(across(
    all_of(col_check),
    ~if_else(.x == "", NA_character_, .x)),
    human_match_judgement = case_when(!is.na(human_manuscript_content) &
                                        is.na(human_match_judgement) ~99,
                                      is.na(human_manuscript_content) &
                                        is.na(human_match_judgement) ~NA,
                                      .default = human_match_judgement),
    # I consider the meaningless ""-> NA change not a correction but a question of reading in the data
    corrected = if_else(human_match_judgement == 99, TRUE, FALSE))

# sanity check
post <- df |> filter(human_match_judgement == 99) |>
  count() 

compare(pre,post)
```

```{r}

# NEW sanity check #
df |> count(codebot_human_agreement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(human_match_judgement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(codebot_match_judgement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> filter(exclude == FALSE) |> 
  count(codebot_human_agreement)|> 
  kable() |> 
  kable_styling()
```

::: callout-caution
The number of valid \[1,0\] codebot_human_agreement ratings is still 1001. Following my logic to include 99 as a valid judgement call indicating indecisiveness, the number of valid observations by the human increased by 85. As intended, the number of valid \[1,0\] CodeBot match judgements remains unchanged as intended.
:::

## CodeBot_match_judgement

```{r}
# sanity check
pre <- df |> 
  filter(is.na(codebot_match_judgement) & !codebot_manuscript_content == "") |> 
  count()

# col_check vector for CodeBot stuff
col_check_c <- df |> 
  colnames() |> 
  as_tibble() |> 
  filter(str_starts(value,"codebot")) |> 
  pull() |> 
  head(-1) |> 
  dput()

# differentiate between meaningful and meaningless NAs
df <- df |> 
  mutate(across(
    all_of(col_check_c),
    ~if_else(.x == "", NA, .x)),
    codebot_match_judgement = case_when(!is.na(codebot_manuscript_content) &
                                          is.na(codebot_match_judgement) 
                                        ~99,
                                        is.na(codebot_manuscript_content) &
                                          is.na(codebot_match_judgement) 
                                        ~NA,
                                        .default = codebot_match_judgement),
    corrected = if_else(codebot_match_judgement == 99, 
                        TRUE, 
                        FALSE)
  )

# sanity check
post <- df |> filter(codebot_match_judgement == 99) |>
  count() 

compare(pre,post)
```

```{r}

# NEW sanity check #
df |> count(codebot_human_agreement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(human_match_judgement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(codebot_match_judgement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> filter(exclude == FALSE) |> 
  count(codebot_human_agreement)|> 
  kable() |> 
  kable_styling()
```

::: callout-caution
The number of valid \[1,0\] codebot_human_agreement ratings is 1001. Following my logic to include 99 as a valid judgement call indicating indecisiveness, the number of valid calls by the human increased by 85 and the number of valid CodeBot match judgements increased by 442. The sum of valid CodeBot judgements is now 1768, which is the exact value reported in the thesis.
:::

## Codebot_human_agreement

In cases where both raters rated NA in the meaningful sense of 99, the agreement should be a match (1) instead of NA. NA for this variable means that less than two ratings total were recorded (only CodeBot/no human vs. only human/no CodeBot vs. neither provided ratings).

```{r}
df <- df |>
  mutate(codebot_human_agreement = if_else(human_match_judgement == 99 &
                                             codebot_match_judgement == 99 &
                                             !is.na(codebot_brief_description) &
                                             !is.na(human_manuscript_content), 
                                           1, 
                                           codebot_human_agreement),
         corrected = if_else(human_match_judgement == 99 &
                               codebot_match_judgement == 99 &
                               !is.na(codebot_brief_description) &
                               !is.na(human_manuscript_content),
                             TRUE,
                             FALSE))

```

::: callout-important
The number of valid \[1,0\] codebot_human_agreement ratings is now **1011**. This is where the error occurred: I only changed the codebot_human_agreement rating for those cases where both ratings were 99. This way, I involuntarily **dropped 318** cases where both raters provided valid ratings but only one of them rated 99 (i.e. 99\|0; 99\|1 and vice versa - see last two sanity checks in this script).
:::

```{r}
# NEW sanity check #
df |> count(codebot_human_agreement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(human_match_judgement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(codebot_match_judgement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> filter(exclude == FALSE) |> 
  count(codebot_human_agreement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(human_match_judgement == 99 & codebot_match_judgement %in% c(1,0))|>  
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> count(human_match_judgement %in% c(1,0) & codebot_match_judgement == 99)|> 
  kable() |> 
  kable_styling()
```

# Correct Error

```{r}
df <- df %>%
  mutate(codebot_human_agreement = case_when(human_match_judgement == 99 & 
                                               codebot_match_judgement == 1 ~ 0,
                                             human_match_judgement == 99 &
                                               codebot_match_judgement == 0 ~ 0,
                                             human_match_judgement == 1 &
                                               codebot_match_judgement == 99 ~ 0,
                                             human_match_judgement == 0 &
                                               codebot_match_judgement == 99 ~ 0,
                                             .default =codebot_human_agreement),
         corrected = if_else(human_match_judgement == 99 &
                               codebot_match_judgement == 99 &
                               !is.na(codebot_brief_description) &
                               !is.na(human_manuscript_content),
                             TRUE,
                             FALSE))

```

```{r}
# NEW sanity check #
df |> count(codebot_human_agreement)|> 
  kable() |> 
  kable_styling()

# NEW sanity check #
df |> filter(exclude == FALSE) |> 
  count(codebot_human_agreement)|> 
  kable() |> 
  kable_styling()
```

::: callout-caution
This additional step recovered the 10+314 = 324 (exclude == FALSE) i.e. 11+318 = 329 (without the exclusion filtering) observations that were previously dropped.
:::

# Save processed Dataframe

```{r}
write_rds(df, "../../data/processed/main/res_main_corrigendum.rds")
```

# Session info

```{r}
devtools::session_info()
```
