---
title: "Main Data Processing"
author: "Anna T. Wittmann"
date: today
format:
  html:
    code-fold: false
    highlight-style: haddock
    theme: flatly
    toc: true
    toc-location: left
execute:
  warning: false
  message: false
---

```{r}
#| label: setup
#| include: false
# Turn off scientific notation globally
options(scipen = 999)
rm(list = ls())
```

# Dependencies

```{r}
# packages and setup 
library(dplyr) # NOTE: needs dplyr version >= 1.2.0 for recode_values() 
library(janitor)
library(kableExtra)
library(readr)
library(stringr)
library(waldo)
library(readxl)
library(purrr)
```

# Read Human Data

```{r}
## read in sheet names
#sheets <- excel_sheets("../../data/raw/main/human/sample_coding_human.xlsx") 
#
## remove cols sample papers and vars
#sheets <- sheets[3:19]
#
## save each sheet as separate df
#sheets |> 
#  set_names() |> 
#  map(~ read_excel("../../data/raw/main/human/sample_coding_human.xlsx", sheet = .x)) |> 
#  list2env(envir = .GlobalEnv)
  
```
## Clean Col Names in Carvalho

```{r}
## vector of abbreviated col names in carvalho
#carv_col <- colnames(carvalho)
#
## vector of correct col names 
#yeung_col <- colnames(yeung)
#
## replace col names
#carvalho |> 
#  colnames() <- yeung_col
#
## check replacement
#colnames(carvalho) == colnames(yeung)
```

```{r}
#cha <- 
#  cha |> 
#  mutate(data_available = as.character(data_available))
#
#carvalho <- 
#  carvalho |> 
#  mutate(data_needed = as.character(data_needed),
#         data_available = as.character(data_available))
#
#akan <- 
#  akan |> 
#  mutate(data_needed = as.character(data_needed),
#         data_available = as.character(data_available))
#
#muenster <- 
#  muenster |> 
#  mutate(data_needed = as.character(data_needed),
#         data_available = as.character(data_available))
```

# Bind all Dataframes

```{r}
#df_human <- bind_rows(list(hussey, bloy, yang, yeung, 
#                  evans, radtke, besken, berger, 
#                  cha, carvalho, akan, muenster, 
#                  nguyen, avilles, hsieh, helm, mancassola),
#                  .id = "paper_id")
#
#df_human |> count(manuscript_content == "NA")
#
#df_human <- df_human |> 
#  mutate(manuscript_content = if_else(manuscript_content == "NA", 
#                                      NA_character_,
#                                      manuscript_content))
```

# Inspect Dataset

```{r}
## identify number of unique analyses
#
#analyses <- df_human |> 
#  group_by(paper_id, analysis_id) |> 
#  count(analysis_id) |> 
#  nrow()
#
## maximum number of possible observations resulting from the dimension x analysis x author structure
#
#obs <- nrow(df_human)
#
## number of observations where I did not find any information
#
#na <- df_human |> 
#  filter(is.na(manuscript_location)) |> 
#  nrow()
```


# Read in Data from CodeBot's Combined Reports & Rough Cleanup

```{r}
#| output: false

# save file paths to vector
files <- dir("../../data/raw/main/adjudicator/combined_reports", 
             full.names = TRUE) |> 
  dput()

# save first authors to vector
author <- dir("../../data/raw/main/adjudicator/combined_reports", 
              full.names = FALSE) |> 
  dput() |> 
  str_remove_all("_combined_report.csv")

# paper_id
paper_id <-  c(1:17)

# read in all .csv() files and combine to one df
df <- read_csv(files, 
               id = "filename",
               na = "null",
               locale = locale(encoding = "UTF-8")) |> 
  # add author column
  mutate(paper_id = dplyr::recode_values(filename, 
                                         from = files, 
                                         to = paper_id),
         # without the dplyr:: there appears to be a namespace collision
         author = dplyr::recode_values(filename, 
                                       from = files, 
                                       to = author)) |>
  # move author column to the front
  relocate(c(author,paper_id), .after = filename)

```

# Check for Empty Rows

This check was predefined in the pre-registration.

```{r}
# remove empty rows
test <- df |> janitor::remove_empty(which = "rows")

# compare df with and without the empty rows
compare(test,df)

# remove from environment
rm(test) 
```

# Rowwise Sanity Check

```{r}
# is paper ID in c(1:17)
df |> 
  count(paper_id)
# yes
```

```{r}
# is analysis ID a number bigger than 1
df |> 
  count(analysis_id)
# yes
```

```{r}
# are there only four dimensions?

df |> 
  count(dimension)
```

```{r}
# are there more than four dimensions?
df |> group_by(dimension) |> 
  count(dimension) |> 
  kable() |> 
  kable_classic(full_width = FALSE)

# correct dimensions and flag corresponding rows
df <- df |> 
  mutate(corrected = if_else(str_detect(dimension, "\\d"), TRUE, FALSE),
         dimension = str_remove(dimension,"\\d"))

df |> group_by(dimension) |> 
  count(dimension) |> 
  kable() |> 
  kable_classic(full_width = FALSE)
```

```{r}
# are there any human_manuscript_entries that are not NA_character or Quotes?
df |> 
  count(human_manuscript_content)
# there are 4 "NA\r\n" resulting from a read in error

# are there NA cells?
df |> 
  count(is.na(human_manuscript_content))
# there are no NA cells

# are there empty cells?
df |> 
  count(human_manuscript_content == "")
# 975 empty cells

# change empty cells to NA, fix read-in error, mark as corrected
df <- df |> 
  mutate(corrected = if_else(human_manuscript_content %in% c("","NA\r\n"), 
                             TRUE, FALSE),
         human_manuscript_content = if_else(human_manuscript_content %in% c("","NA\r\n"),
                                            NA, human_manuscript_content))
```

```{r}
# is the manuscript location only numbers between 0 and 3?
df |> 
  count(human_manuscript_location)
# 978 empty rows and and four NA\r\n

# change empty cells to NA, fix read-in error, mark as corrected
df <- df |> 
  mutate(corrected = if_else(human_manuscript_location %in% c("","NA\r\n"), 
                             TRUE, FALSE),
         human_manuscript_location = if_else(human_manuscript_location %in% c("","NA\r\n"),
                                            NA, human_manuscript_location))
```

```{r}
df |> 
  count(human_code_content)

df |> 
  count(human_code_content %in% c("NA\r\n", ""))
# 1479 empty rows and and NA\r\n

# change empty cells to NA, fix read-in error, mark as corrected
df <- df |> 
  mutate(corrected = if_else(human_code_content %in% c("","NA\r\n"), 
                             TRUE, FALSE),
         human_code_content = if_else(human_code_content %in% c("","NA\r\n"),
                                            NA, human_code_content))
```
```{r}
df |> 
  count(human_code_location)

df |> 
  count(human_code_location %in% c("NA\r\n", ""))
# 806 empty rows and and NA\r\n

# change empty cells to NA, fix read-in error, mark as corrected
df <- df |> 
  mutate(corrected = if_else(human_code_location %in% c("","NA\r\n"), 
                             TRUE, FALSE),
         human_code_location = if_else(human_code_location %in% c("","NA\r\n"),
                                            NA, human_code_location))
```

```{r}
df |> 
  count(human_match_judgement)
```
human_match_judgement should only be NA when human_manuscript_content is NA.

```{r}
df |> 
  filter(is.na(human_manuscript_content)) |> 
  count(human_match_judgement)
```
when hmj is NA even though hmc is not, hmj should be 99 to clearly distinguish between indesisiveness and missingness.

```{r}
df <- df |> 
  mutate(exclude = if_else(is.na(human_manuscript_content) &
                    !is.na(human_match_judgement), TRUE, FALSE),
         human_match_judgement = case_when(is.na(human_manuscript_content) & 
                                             is.na(human_match_judgement) ~ NA,
                                           !is.na(human_manuscript_content) & 
                                             is.na(human_match_judgement) ~ 99,
                                           is.na(human_manuscript_content) &
                                             !is.na(human_match_judgement) ~ NA,
                                           .default = human_match_judgement))
# there should now be the same amount of NA and 85 "99"
df |> 
  count(human_match_judgement)
# yes
```

```{r}
df |> 
  count(codebot_brief_description %in% c("", NA))

df <- df |> 
  mutate(codebot_brief_description = if_else(codebot_brief_description == "", 
                                             NA, codebot_brief_description))

df |> 
  count(is.na(codebot_brief_description))
```
```{r}
# same for manuscript content

df |> 
  count(codebot_manuscript_content %in% c("", NA))

df <- df |> 
  mutate(codebot_manuscript_content = if_else(codebot_manuscript_content == "", 
                                             NA, codebot_manuscript_content))

df |> 
  count(is.na(codebot_manuscript_content))

```

```{r}
df |> 
  count(codebot_manuscript_location)
```
```{r}
# same for code content

df |> 
  count(codebot_code_content %in% c("", NA))

df <- df |> 
  mutate(codebot_code_content = if_else(codebot_code_content == "", 
                                             NA, codebot_code_content))

df |> 
  count(is.na(codebot_code_content))

```
```{r}
df |> 
  filter(!is.na(codebot_manuscript_content)) |> 
  count(codebot_match_judgement)

df <- df |> 
  filter() |> 
  mutate(codebot_match_judgement = case_when(is.na(codebot_manuscript_content) &
                                              is.na(codebot_match_judgement) ~ NA,
                                             !is.na(codebot_manuscript_content) &
                                              is.na(codebot_match_judgement) ~ 99,
                                             .default = codebot_match_judgement),
         corrected = if_else(codebot_match_judgement == 99, TRUE, FALSE))
# there should now be the same amount of NA and 85 "99"
df |> 
  count(codebot_match_judgement)
# yes
```
# correct codebot_human_agreement
```{r}
df |> 
  group_by(codebot_match_judgement, human_match_judgement, codebot_human_agreement) |> 
  count()
```
whenever both raters provided ratings of either [1,0,99] codebot_human_agreement should not be NA.
it should only be NA when only one or neither of the two raters provided valid ratings.

```{r}
df <- df |> 
  mutate(codebot_human_agreement = case_when(is.na(codebot_match_judgement) &
                                               is.na(human_match_judgement) ~ NA,
                                             is.na(codebot_match_judgement) |
                                               is.na(human_match_judgement) ~ NA,
                                             codebot_match_judgement == human_match_judgement ~ 1,
                                             !codebot_match_judgement == human_match_judgement ~ 0,
                                             .default = codebot_human_agreement))

df |> 
  group_by(codebot_match_judgement, human_match_judgement, codebot_human_agreement) |> 
  count()
```


# Check for Human Error in Manually Coded Entries

After visually inspecting the data, it is evident that there are multiple sources of minor, fixable errors introduced by a) manual coding, b) working with the .csv files across different operating systems c) the adjudication programming. The following reflects my attempt to clean up the data as best as I can with the limitation that there is no second set of eyes to validate my approach. Rows containing (minorly) modified observations will get flagged in a separate boolean variable *corrected*. Another boolean variable (*exclude*) will flag observations with major issues that warrant exclusion from the inferential analyses. See below a list of spotted data quality issues after visually inspecting the data and comparing it to the sample_coding_human.xlsx file.

::: callout-caution
While the first source of error was anticipated in the pre-registration, this was not the case for the latter two. However, I consider the assessment of the latter error sources to be crucial for the validity of the results which is why I will flag them during processing.
:::

**List of observed errors:**

-   In the data from Hsieh et al., the columns manuscript_content through results for the inference criteria were coded as `NA\r\n`. Since the `\r\n` part are Window's "invisible" characters signaling Carriage Return `\r` and Line Feed `\n`, they create the weird situation where those cells are neither recognized by is.na() nor by directly filtering for "NA". Apparently, read_csv() also did not recognize them as NA_characters and neither did the adjudicator which was supposed to replace rows which only had NAs with empty strings throughout. NA:NA in human_code_location resulted from the adjudicator aggregating across the given file and code line quote. This should also be empty instead of NA. -\> Change these cells to "" (because the NA coding needs to be fixed later).

-   Inconsistent use of delimiters when it comes to manuscript location quotes - Missing manuscript content in cases where manuscript location and a judgement are given and a comparison to the original excel sheet makes it evident that there must have been a copy & paste error involved -\> Flag but do not correct because this would alter the adjudicator's judgement.

-   Dimensions were numbered for clarity during manual coding, not all numbers were removed.

Screening for human_manuscript_content cells unintentionally left blank.

```{r}
df |> 
  filter(is.na(human_manuscript_content) & str_detect(human_manuscript_location,"\\d"))


```

In case of Berger et el., there are 3 misplaced location quotes, all for the variable "single item america" as is evident from the sample_coding_human.xlsx which should be empty strings instead. Carvalho et al. is missing the following transformation quote: "Accuracy by question type and a total score was calculated". Going back to the paper, the Evans quote is wrong since there was no mention of a transformation to be found. Going back to Helm revealed, that there were multiple problematic lines. For Analysis 2, the inference criterion is in fact not evident from the text. The inference criterion for Analyses 3 and 4 should be "95% CI". For Mancassola, the quotes for variable specification are missing in analyses 5 to 8 due to a manual copy pasting error since they required the same quote as the model specification which is always given.

::: {callout-note}
I will not fill the blanks for manuscript content since their absence impacted the adjudicator's judgement. I also choose not to correct the respective adjudicator's judgements manually, because I cannot account for possible distortion of the adjudicator's ratings. Instead, I will mark them as to be excluded in the GLMM analysis.
:::

```{r}
# add exclusion variable
df <- df |>  
  mutate(exclude = if_else(is.na(human_manuscript_content)&
                             str_detect(human_manuscript_location,"\\d"),
                           TRUE,
                           FALSE))

# sanity check
df |> 
  filter(exclude == TRUE) |> 
  count() |> 
  pull()
```

# Sanity Check NAs

Currently, there is an issue with the meaning of NAs across the 3 judgement variables.

**Human_match_judgement** takes on this value both when manuscript information is present and when it is not. This should not be the case as an NA in the sense of "indecisiveness" is different from NA in the sense of missingness. I will change meaningful NAs to 99 and cases where there is no manuscript content coded to NA. Once the match variable has been transformed, I will replace human_match_judgement with NA whenever no quote was provided so that NA truly reflects absence and 99 uncertainty.

**Codebot_match_judgement** takes on the values 1/0/NA and there are no empty string entries by CodeBot. Thus the match judgement will become 99 in cases where it was previously NA.

**Codebot_human_agreement** is currently NA in cases where both raters rated "meaningful" NA but also NA when one rater's info is missing. Cases where one rater's rating is missing should stay NA because it indicates the absence of assessable agreement, but cases where both raters coded info and judged "meaningful" NA, the adjudicator's rating should be 99.

# Save processed Dataframe

```{r}
write_rds(df, "../../data/processed/main/res_main_correction1.rds")
```

# Session info

```{r}
devtools::session_info()
```
